Davos: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2023-09-30 paper/main.tex
updates to fig 1 caption

\begin{figure}[tp]
\centering
\includegraphics[width=0.65\textwidth]{figs/shareable_code_2d}
\caption{\small \textbf{Systems for sharing code within the Python
  ecosystem.}  The $x$-axis denotes the ``burden'' placed on users to
  install and configure the given system (systems placed further to the right, that fall within the redder shading, impose a higher setup cost on the user).  The $y$-axis denotes the
  degree to which the system guarantees that the code will run
  similarly for different users (systems placed higher up, that fall within the bluer shading, support stronger guarantees).
  From left to right, bottom to top: plain-text \textbf{Python
  scripts} (\texttt{.py} files) provide the most basic ``system''
  for sharing raw code.  Scripts may reference external packages, but
  those packages must be manually installed on other users' systems.
  Further, any checking needed to verify that the correct versions of
  those packages were installed must also be performed manually.
  \textbf{Jupyter notebooks} (\texttt{.ipynb} files) comprise embedded
  text, executable code, and media (including rendered figures, code
  output, etc.).  When the \textbf{Davos package} is imported
  into a Jupyter notebook, the notebook's functionality is extended to
  automatically install any required external packages (at their
  correct versions, when specified).  \textbf{Virtual environments}
  allow users to install an isolated copy of Python and all required
  dependencies. This typically entails distributing a configuration
  file (e.g., a \texttt{pyproject.toml}~\cite{CannEtal16} or
  \texttt{environment.yml} file) that specifies all project
  dependencies (including version numbers of external packages)
  alongside the primary code base. Users can then install a
  third-party tool~\cite[e.g.,][]{Anac12, Eust19} to read the file and
  build the environment.  \textbf{Containers} provide a means of
  defining an isolated environment that includes a complete operating
  system (independent of the user's operating system), in addition to
  (optionally) specifying a virtual environment or other
  configurations needed to provide the necessary computing
  environment.  Containers are typically defined using specification
  files (e.g., a plain-text \texttt{Dockerfile}) that instruct the
  virtualization engine regarding how to build the containerized
  environment.  \textbf{Virtual machines} provide a complete
  hardware-level simulation of the computing environment.  In addition
  to simulating specific hardware, virtual machines (typically
  specified using binary image files) must also define operating
  system-level properties of the computing environment.  Systems to
  the left of the blue vertical line entail sharing individual files,
  with no additional installation or configuration needed to run the
  target code.  Systems to the right of the red vertical line support
  precise control over dependencies and versioning.  Notebooks
  enhanced using the Davos package are easily shareable and
  require minimal setup costs, while also facilitating high
  reproducibility by enabling precise control over project
  dependencies.}
\label{fig:code-sharing}
\end{figure}

>>>>

\begin{figure}[tp]
\centering
\includegraphics[width=0.65\textwidth]{figs/shareable_code_2d}
\caption{\small \textbf{Systems for sharing code within the Python
  ecosystem.} The $x$-axis denotes the ``burden'' placed on users to
  install and configure the given system (systems placed further to the right, that fall within the redder shading, impose a higher setup cost on the user).  The $y$-axis denotes the
  degree to which the system guarantees that the code will run
  similarly for different users (systems placed higher up, that fall within the bluer shading, offer stronger guarantees).
  From left to right, bottom to top: plain-text \textbf{Python
  scripts} (\texttt{.py} files) provide the most basic ``system''
  for sharing raw code.  Scripts may reference external packages, but
  those packages must be manually installed on other users' systems.
  Further, any checking needed to verify that the correct versions of
  those packages were installed must also be performed manually.
  \textbf{Jupyter notebooks} (\texttt{.ipynb} files) comprise embedded
  text, executable code, and media (including rendered figures, code
  output, etc.). When the \textbf{Davos package} is imported
  into a Jupyter notebook, the notebook's functionality is extended to
  automatically install any required external packages (at their
  correct versions, when specified) into an isolated directory kept separate
  from the user's existing set of packages. \textbf{Virtual environments}
  similarly allow users to install required packages into an isolated
  directory, and \textbf{shareable Python environments} extend this to include
  a specific version of Python itself. However, both of these systems require
  users to create, populate, and manage environments manually. This
  typically entails distributing a configuration file (e.g., a
  \texttt{requirements.txt}, \texttt{pyproject.toml}~\cite{CannEtal16}, or
  \texttt{environment.yml} file) that specifies all project dependencies
  (including version numbers) alongside the primary code base. Users can then
  install a third-party tool~\cite[e.g.,][]{BickEtal07, Eust19, Anac12} to read
  the file and build the environment. \textbf{Containers} provide a means of
  defining an isolated environment that includes a complete operating
  system (independent of the user's operating system), in addition to
  (optionally) specifying a virtual environment or other
  configurations needed to provide the necessary computing
  environment. Containers are typically defined using
  specification files (e.g., a plain-text \texttt{Dockerfile}~\cite{Merk14}) that instruct the
  virtualization engine regarding how to build the containerized
  environment. \textbf{Virtual machines} provide a complete
  hardware-level simulation of the computing environment.  In addition
  to simulating specific hardware, virtual machines (typically
  specified using binary image files) must also define operating
  system-level properties of the computing environment.  $\Delta_1$
  represents the increased reproducibility Davos provides over standard
  Jupyter notebooks for no greater setup cost. $\Delta_2$ represents
  Davos's lower setup cost compared to standard virtual environments
  despite more stringently ensuring reproducibility.}
\label{fig:code-sharing}
\end{figure}
